---
title: "Butt SWAT Review"
author: "Capt Spencer Butt"
date: "March 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Review Date and Time

* Review Date: 12 March 2018
* Review Time: 1045


## Accuracy

* **Instructions**
    + Clear documentation regarding usage
    + Each step in analysis is clearly documented
    + Examples are shown/provided in instructions makes usage easy
* **Load Data**
    + Data loads without any issue
    + Progress bar is very helpful
    + `Input and clean` button provides helpful user feedback and validates that data is loaded correctly
    + Displaying the data table after load is useful user feedback
* **Exploratory Data Analysis**
    + Bar charts display data as expected
    + Density plots and filters work as expected
    + No major accuracy concerns with data visualization
* **Community Detection**
    + Line plots are displayed as expected
    + No accuracy concerns
* **Community Domains**
    + All plotting and display functionality works as intended
    + No accuracy concerns

## Compliation

There was only one **minor** error encountered during review. The following error was encountered whenever the `Input and Clean` tab was selected after data was imported for use in SWAT:

```{r Error, eval = FALSE, echo = TRUE }
Listening on http://127.0.0.1:3185
Warning: Error in FUN: object 'referrer' not found
Stack trace (innermost first):
    113: FUN
    112: FUN
    111: lapply
    110: f
    109: l$compute_aesthetics
    108: f
    107: by_layer
    106: ggplot_build
    105: print.ggplot
    104: print
    103: print
    102: renderPlot [C:\Users\thebu\OneDrive\Documents\R\win-library\3.4\SWAT\apps\SWAT/server.R#163]
     92: <reactive:plotObj>
     81: plotObj
     80: origRenderFunc
     79: output$barchart
      4: <Anonymous>
      3: do.call
      2: print.shiny.appobj
      1: <Promise>
```

This error did not result in any adverse performance of the analytic product. It was displayed only in the console window as information to the user. All other processes worked as expected and displayed no errors. The package downloaded and compiled without any errors.

## Ease of Use

SWAT was well documented and extremely easy to use. There was never a question to what action to perform next, nor was there a question of what analysis was happening in the background of the program. All SWAT functions worked as intended and there were no problems encountered resulting in the programming crashing. 

## Final Thoughts

SWAT is extremely well made and would be useful for both intelligence analysts and 61A/ORSAs. The program is well documented and aside from the one informational error which is minor, SWAT is an **Outstanding** analytic product.

**Recommended Grade:** 50/50

